Consensus Problems in Networks of Agents\\ with Switching Topology and Time-Delays

### 2020-10-26 Paper.tex
Complete Chapter 5

\section{Introduction}
{\color[gray]{0.5}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].
}

@@

\section{Consensus Problems}
{\color[gray]{0.5}
Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a weighted directed graph (or digraph) with $n$ nodes and a weighted adjacency matrix $\mathcal{A}=[a_{ij}]$ where $a_{ij} \ge 0$ for all $i,j \in \mathcal{I}={1,2,…,n}$ with $i \ne j$. 
Here, $\mathcal{V}$ denotes the set of vertices $v_i$ and $\mathcal{E}$ denotes the set of edges $ij$ (or ($v_i,v_j$)) of the graph $G$. 
The set of neighbors of node $i$ is denoted by $N_i=\{ij\in \mathcal{E}:a_{ij}>0\}$. 
We call any subset of nodes $J$ a cluster. 
The set of neighbors of a cluster $J\subset \mathcal{I}$ is deﬁned by
}

@@

\section{Consensus Protocols}
{\color[gray]{0.5}
\noindent In this section, we present three consensus protocols that solve agreement problems in a network of continuous-time (CT) {\color{green}integrator agents} with dynamics
}

@@

\section{Algebraic Graph Theory: Properties of Laplacians}
{\color[gray]{0.5}
\noindent In this section, we introduce some basic concepts and notation in graph theory that will be used throughout the paper. 
More information is available in [11, 5]. 
A comprehensive survey on properties of Laplacians of undirected graphs can be found in [17]. 
However, we need to work with Laplacians of directed graphs that the basic properties cannot be found in graph theory literature and will be stated here.
}

@@

\section{A Counterexample for Average-Consensus}
在推论1（Corollary 1）协议中，所有节点的每个决策值$\alpha$等于$\text{Ave}(x(0))$的充分条件是$\sum_{i=1}^{n}u_i \equiv 0$。
如果图$G$是无向图（即$a_{ij}=a_{ji} > 0,\forall i,j: a_{ij}\ne 0$），自动的情况$\sum_{i=1}^{n}u_i=0$，$\forall x$和$\text{Ave}(x(t))$是不变的量，参考文献[20]。
然而，这个性质并不适用于一般有向图。

一个简单的反例就是图(\ref{2})表示的3阶$n=3$强连接图，其中权重在\{0，1\}中，向量和边的集合如下所示：
\begin{equation}
    \mathcal{V} = \{1, 2, 3 \},\quad \mathcal{E}=\{12, 23, 31, 13\}.
    \notag
\end{equation}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=4cm]{figures/Fig2-ConnectedDigraph.jpeg}
    \label{ConnectedDigraph}
    \caption{一个不能使用协议(\ref{A1})解决平均一致性问题的3阶连通图}
\end{figure}

对于图$G=(\mathcal{V}, \mathcal{E})$，$\sum_{i=1}^{3}u_i = x_3 - x_1$。
因此，如果节点1和3不一致，那么属性$\sum_{i=1}^{3}u_i = 0$不是对于所有的$x$都成立。
另一方面，读者可以在本例中来验证这一点
\begin{equation}
    L = \left[
    \begin{matrix}
        2 & -1 & -1 \\
        0 & 1 & -1 \\
        -1 & 0 & 1 
    \end{matrix}
    \right]
    \notag
\end{equation}

{\color{userColor}
\begin{equation}
    D = \left[
    \begin{matrix}
        2 & 0 & 0 \\
        0 & 1 & 0 \\
        0 & 0 & 1 
    \end{matrix}
    \right],
    A = \left[
    \begin{matrix}
        0 & 1 & 1 \\
        0 & 0 & 1 \\
        1 & 0 & 0 
    \end{matrix}
    \right],
    L = D - A
    \notag
\end{equation}
}

并且$x^*_i = [x_1(0) + x_2(0) + 2x_3(0)]/4$（此公式基于Theorem 3）。
这个决策值在所有$x_i(0)$的凸包中是显而易见的，但是当且仅当$x_1(0) + x_2(0) \ne 2x_3(0)$时，决策值不等于$\text{Ave}(x(0))$。
结果就是，对于所有初始条件满足$x_1(0) + x_2(0) \ne 2x_3(0)$，协议(\ref{A1})并不能解决平均一致性问题，但所有的节点仍能达到一致。
这促使我们描述所有的图的类，来解决平均一致性问题。

在提出我们第一次的主要结果之前，我们需要提供一个指数矩阵如$e^{(-Lt)}$形式的极限理论。
这是因为系统(\ref{6})的解决办法是通过以下公式给出
\begin{equation}
    x(t) = exp(-Lt)x(0)
    \tag{17}
    \label{17}
\end{equation}
并且通过对$exp(-Lt)$的显示计算，我们可以获得达到一致性的总图节点的决策值。
在非负矩阵理论中，接下来的定理与著名的极限定理关系密切，即Perron-Frobenius定理（Perron-Frobenius Theorem），参考文献[12]{\color[gray]{0.5}（R. A. Horn and C. R. Johnson. Matrix Analysis. Cambridge University Press, 1987）}。

@@

\noindent \textbf{Theorem 3.} 假设$G$是一个强连通图，拉普拉斯算子$L$满足$Lw_r=0$，$w_l^TL = 0$，$w_l^Tw_r=1$。
\begin{equation}
    R = \lim_{t\rightarrow +\infty} exp(-Lt) = w_r w_l^T \in M_n
    \tag{18}
    \label{18}
\end{equation}
\begin{equation}
    {\color{userColor} \text{R = t趋于无穷时-Lt关于e指数值极限 = 右特征向量 * 左特征向量}}
    \notag
\end{equation}

\noindent \textbf{Proof.} 令$A=-L$，$J$为$A$的约当形，即$A=SJS^{-1}$。
我们有$exp(At) = S\ exp(Jt)\ S^{-1}$当$s\rightarrow +\infty$，$exp(Jt)$收敛至一个具有单一非零元素$q_{11}=1$的矩阵$Q=[q_{ij}]$。
对角矩阵$exp(Jt)$的其他块会变成0，由于对于所有的$k\ge2$，都有$Re(\lambda_k(A))<0$，这里$\lambda_k(A)$是矩阵$A$的第$k$个最大的特征值$|A|$。
注意$R=SQS^{-1}$。
由于$AS=SJ$，$S$的第一列为$w_r$。
相似的，$S^{-1}A = JS^{-1}$，这也意味着$S^{-1}$的第一行是$w_l^T$。
由于$S^{-1}S=T$，$w_l$满足如性质所述的$w_l^Tw_r=1$。
直接的计算显示$R=w_rw_l^T\in M_n$。

\section{Networks with Fixed or Switching Topology}
这部分，我们提出了三种主要的结论：i）描述了所有使用协议(\ref{A1})解决平均一致性问题的连接图。
ii）协议(\ref{A1})的性能和图的费德勒特征值（即代数连接）之间的联系。
iii）在切换拓扑下的连接失败/生成的鲁棒一致性问题。

@@

\section{Networks with Communication Time-Delays}
考虑固定拓扑$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$连续时间网络，其节点$i$的状态经过一个时滞$\tau > 0$的通信通道（或连接）达到节点$j$。
关于连接$ij$的转移函数表示如下：
\begin{equation}
    h_{ij}(s) = e^{-\tau_{ij}s}
    \notag
\end{equation}
应用线性时滞协议(\ref{A2})，网络动态变化可写作：
\begin{equation}
    \dot{x}_i(t) = \sum_{j\in N_i} a_{ij} [x_j(t-\tau_{ij}) - x_i(t-\tau_{ij})].
    \tag{37}
    \label{37}
\end{equation}
通过对公式(\ref{37})两边进行拉氏变换，我们得到
\begin{equation}
    sX_i(s) - x_i(0) = \sum_{j\in N_i} a_{ij} h_{ij}(s) (X_j(s) - X_i(s))
    \tag{38}
    \label{38}
\end{equation}
这里$X_i(s)$表示所有$i\in \mathcal{I}$中$x_i(t)$的拉氏变换。
公式的最后一部分可以写作如下紧凑形式：
\begin{equation}
    X(s) = (s+L(s))^{-1}x(0)
    \tag{39}
    \label{39}
\end{equation}
这里$L(x)$是图关于邻接矩阵$\mathcal{A}(s) = [a_{ij}h_{ij}(s)]$的拉普拉斯矩阵。
总的来说，任何关于通道$ij$的过滤效果都可以合并成连接转换函数$h_{ij}(s)$。
关于通信时滞智能体网络的协议(\ref{A2})收敛性分析减小为一个多输入多输出系统（MIMO）转移函数的稳定性分析
\begin{equation}
    G(s) = (sI+L(s))^{-1}.
    \notag
\end{equation}

@@

\section{Max-Consensus and Leader Determination}
在这部分，我们讨论带有一个唯一的最大领导者（max-leader）网络的最大一致性问题，即节点$i^*=\arg\max_ix_i(0)$。
最大一致性问题描述如下。
每一个智能体都有下述离散模型
\begin{equation}
    \tag{41}
    \label{41}
    x_i(k+1)=max(x_i(k),u_i(k))
\end{equation}
且被称作最大智能体（max-agent）。
最大智能体的动态等价描述为一个非线性离散时间系统如下：
\begin{equation}
    \tag{42}
    \label{42}
    x_i(k+1) = \frac{1}{2}(x_i(k)+u_i(k)+|x_i(k)-u_i(k)|)
\end{equation}
图$G=(\mathcal{V},\mathcal{E})$所有节点的值必须反复收敛到最大领导者的值。
另外，分布式的每一个节点都必须决定其是否是最大领导者。
最大一致性问题的一个应用是决定群组中的领导者（或协调者）具备关于特别兴趣量（例如，序列号，花费，高度，等等）的优先级，其必须执行或协调任务。

@@

\section{Simulation Results}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig4-BalancedSC.jpeg}
    \label{Fig4}
    \caption{强连接的平衡图}
\end{figure}

@@

\section{Conclusions}
我们提供了具备有向信息流和固定或切换拓扑网络的一致性协议的收敛性分析。
我们的分析依赖于一些代数图论和矩阵论的工具。
我们建立了线性一致性协议的性质和镜像图拉普拉斯算子的费德勒特征值之间的联系。
介绍了简单的非一致性函数，其作为李雅普诺夫方程，允许切换拓扑网络的一致性协议的收敛性分析。
给出的交换图，该图表明了平衡图的加权邻接矩阵采用矩阵交换的拉普拉斯算子和对称部分矩阵的运算。
平衡图被证明对解决平均一致性问题是有帮助的。

>>>>

% ------------------------------------------------------------------------------
\section{Introduction}
{\color[gray]{0.5}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].
}

@@

% ------------------------------------------------------------------------------
\section{Consensus Problems}
{\color[gray]{0.5}
Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a weighted directed graph (or digraph) with $n$ nodes and a weighted adjacency matrix $\mathcal{A}=[a_{ij}]$ where $a_{ij} \ge 0$ for all $i,j \in \mathcal{I}={1,2,…,n}$ with $i \ne j$. 
Here, $\mathcal{V}$ denotes the set of vertices $v_i$ and $\mathcal{E}$ denotes the set of edges $ij$ (or ($v_i,v_j$)) of the graph $G$. 
The set of neighbors of node $i$ is denoted by $N_i=\{ij\in \mathcal{E}:a_{ij}>0\}$. 
We call any subset of nodes $J$ a cluster. 
The set of neighbors of a cluster $J\subset \mathcal{I}$ is deﬁned by
}

@@

% ------------------------------------------------------------------------------
\section{Consensus Protocols}
{\color[gray]{0.5}
\noindent In this section, we present three consensus protocols that solve agreement problems in a network of continuous-time (CT) {\color{green}integrator agents} with dynamics
}

@@

% ------------------------------------------------------------------------------
\section{Algebraic Graph Theory: Properties of Laplacians}
{\color[gray]{0.5}
\noindent In this section, we introduce some basic concepts and notation in graph theory that will be used throughout the paper. 
More information is available in [11, 5]. 
A comprehensive survey on properties of Laplacians of undirected graphs can be found in [17]. 
However, we need to work with Laplacians of directed graphs that the basic properties cannot be found in graph theory literature and will be stated here.
}

@@

% ------------------------------------------------------------------------------
\section{A Counterexample for Average-Consensus}
{\color[gray]{0.5}
\noindent A suﬃcient condition for the decision value $\alpha$ of each node in the proof of Corollary 1 to be equal to $\text{Ave}(x(0))$ is that $\sum_{i=1}^{n}u_i \equiv 0$. 
If $G$ is undirected (i.e. $a_{ij}=a_{ji} > 0,\forall i,j: a_{ij}\ne 0$), automatically the condition $\sum_{i=1}^{n}u_i=0$, $\forall x$ holds and $\text{Ave}(x(t))$ is an invariant quantity [20]. 
However, this property does not hold for a general digraph.
}

\noindent 在推论1（Corollary 1）协议中，所有节点的决策值$\alpha$等于$\text{Ave}(x(0))$的充分条件是$\sum_{i=1}^{n}u_i \equiv 0$。
如果图$G$是无向图（即$a_{ij}=a_{ji} > 0,\forall i,j: a_{ij}\ne 0$），自动的情况$\sum_{i=1}^{n}u_i=0$，$\forall x$和$\text{Ave}(x(t))$是不变的量，参考文献[20]。
然而，这个性质并不适用于一般有向图。

{\color[gray]{0.5}
A simple counterexample is a strongly connected digraph of order $n$ = 3, shown in Figure 2, with weights in \{0, 1\} and the following sets of vertices and edges:
}

一个简单的反例就是图(\ref{2})表示的3阶$n=3$强连接图，其中权重在\{0，1\}中，向量和边的集合如下所示：

\begin{equation}
    \mathcal{V} = \{1, 2, 3 \},\quad \mathcal{E}=\{12, 23, 31, 13\}.
    \notag
\end{equation}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4cm]{figures/Fig2-ConnectedDigraph.jpeg}
    \label{ConnectedDigraph}
    \caption{一个不能使用协议(\ref{A1})解决平均一致性问题的3阶连通图}
\end{figure}

{\color[gray]{0.5}
For the digraph $G=(\mathcal{V}, \mathcal{E})$, $\sum_{i=1}^{3}u_i = x_3 - x_1$. 
Thus, if nodes 1 and 3 disagree, the property $\sum_{i=1}^{3}u_i = 0$ does not hold for all $x$. 
On the other hand, the reader can verify that for this example
}

对于图$G=(\mathcal{V}, \mathcal{E})$，$\sum_{i=1}^{3}u_i = x_3 - x_1$。
因此，如果节点1和3不一致，那么属性$\sum_{i=1}^{3}u_i = 0$不是对于所有的$x$都成立。
另一方面，读者可以在本例中来验证这一点

\begin{equation}
    L = \left[
    \begin{matrix}
        2 & -1 & -1 \\
        0 & 1 & -1 \\
        -1 & 0 & 1 
    \end{matrix}
    \right]
    \notag
\end{equation}

% {\color{userColor}
% \begin{equation}
%     D = \left[
%     \begin{matrix}
%         2 & 0 & 0 \\
%         0 & 1 & 0 \\
%         0 & 0 & 1 
%     \end{matrix}
%     \right],
%     A = \left[
%     \begin{matrix}
%         0 & 1 & 1 \\
%         0 & 0 & 1 \\
%         1 & 0 & 0 
%     \end{matrix}
%     \right],
%     L = D - A
%     \notag
% \end{equation}
% }

{\color[gray]{0.5}
\noindent and $x^*_i = [x_1(0) + x_2(0) + 2x_3(0)]/4$ (this is due to Theorem 3). 
This decision value is apparently in the convex hull of all the $x_i(0)$’s but it is diﬀerent from $\text{Ave}(x(0))$ if and only if $x_1(0) + x_2(0) \ne 2x_3(0)$. 
As a result, for all initial conditions satisfying $x_1(0) + x_2(0) \ne 2x_3(0)$, Protocol (A1) does not solve the average-consensus problem but still all nodes reach an agreement. 
This motivates us to characterize the class of all digraphs that solve the average-consensus problem.
}

\noindent 并且$x^*_i = [x_1(0) + x_2(0) + 2x_3(0)]/4$（此公式源于Theorem 3）。
显而易见的这个决策值包含在所有$x_i(0)$的凸包中，但是当且仅当$x_1(0) + x_2(0) \ne 2x_3(0)$时，决策值不等于$\text{Ave}(x(0))$。
结果就是，对于所有满足$x_1(0) + x_2(0) \ne 2x_3(0)$的初始情况，协议(\ref{A1})并不能解决平均一致性问题，但所有的节点仍能达到一致。
这促使我们来描述所有的图的类，以解决平均一致性问题。

{\color[gray]{0.5}
Before presenting our ﬁrst main result, we need to provide a limit theorem for exponential matrices of the form $e^{(-Lt)}$. 
This is because the solution of (6) is given by
}

在提出我们第一次的主要结果之前，我们需要提出一个指数矩阵如$e^{(-Lt)}$形式的极限理论。
这是因为系统(\ref{6})的解决办法是通过以下公式给出

\begin{equation}
    x(t) = exp(-Lt)x(0)
    \tag{17}
    \label{17}
\end{equation}

{\color[gray]{0.5}
\noindent and by explicit calculation of $exp(-Lt)$, we can obtain the decision value of each node after reaching consensus for a general digraph. 
The following theorem is closely related to a famous limit theorem in the theory of nonnegative matrices known as Perron-Frobenius Theorem [12].
}

\noindent 并且通过对$exp(-Lt)$的显示计算，我们可以得到普通图在达到一致性后每个节点的决策值。
接下来的定理在非负矩阵理论中与著名的极限定理关系密切，即Perron-Frobenius定理（Perron-Frobenius Theorem）[12]。

{\color[gray]{0.5}
\noindent \textbf{Notation.} Following the notation in [12], we denote the set of $m\times n$ real matrices by $M_{m,n}$  and the set of square $n\times n$ matrices by $M_n$ . 
Furthermore, throughout this paper, the right and left eigenvectors of the Laplacian $L$ associated with $\lambda_1 = 0$ are denoted by $w_r$ and $w_l$ , respectively.
}

@@

{\color[gray]{0.5}
\noindent \textbf{Theorem 3.} Assume $G$ is a strongly connected digraph with Laplacian $L$ satisfying $Lw_r=0$，$w_l^TL = 0$，$w_l^Tw_r=1$. Then
}

\noindent \textbf{Theorem 3.} 假设$G$是一个强连通图，拉普拉斯矩阵$L$满足$Lw_r=0$，$w_l^TL = 0$，$w_l^Tw_r=1$。那么

\begin{equation}
    R = \lim_{t\rightarrow +\infty} exp(-Lt) = w_r w_l^T \in M_n
    \tag{18}
    \label{18}
\end{equation}

% \begin{equation}
%     {\color{userColor} \text{R = t趋于无穷时-Lt关于e指数值极限 = 右特征向量 * 左特征向量}}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent \textbf{Proof.} Let $A=-L$ and let $J$ be the Jordan form associated with $A$, i.e. $A=SJS^{-1}$ . 
We have $exp(At) = S\ exp(Jt)\ S^{-1}$ and as $s\rightarrow +\infty$, $exp(Jt)$ converges to a matrix $Q=[q_{ij}]$ with a single nonzero element $q_{11}=1$. 
The fact that other blocks in the diagonal of $exp(Jt)$ vanish is due to the property that $Re(\lambda_k(A))<0$ for all $k\ge2$ where $\lambda_k(A)$ is the $k$th largest eigenvalue of $A$ in terms of magnitude $|\lambda_k|$ . 
Notice that $R=SQS^{-1}$ . 
Since $AS=SJ$ the ﬁrst column of $S$ is $w_r$ . 
Similarly, $S^{-1}A = JS^{-1}$ that means the ﬁrst row of $S^{-1}$ is $w_l^T$. 
Due to the fact that $S^{-1}S=I$, $w_l$ satisﬁes the property $w_l^Tw_r=1$ as stated in the question. 
A straightforward calculation shows that $R=w_rw_l^T\in M_n$.
}

\noindent \textbf{Proof.} 令$A=-L$，$J$为$A$的约当形，即$A=SJS^{-1}$。
我们有$exp(At) = S\ exp(Jt)\ S^{-1}$当$s\rightarrow +\infty$，$exp(Jt)$收敛至一个含有单一非零元素$q_{11}=1$的矩阵$Q=[q_{ij}]$。
对角矩阵$exp(Jt)$的其他块会变成0，由于对于所有的$k\ge2$，都有$Re(\lambda_k(A))<0$，这里$\lambda_k(A)$是矩阵$A$关于$|\lambda_k|$的第$k$个最大的特征值。
注意$R=SQS^{-1}$。
由于$AS=SJ$，$S$的第一列为$w_r$。
相似的，$S^{-1}A = JS^{-1}$，这也意味着$S^{-1}$的第一行是$w_l^T$。
由于$S^{-1}S=I$，$w_l$满足如问题中所述的性质$w_l^Tw_r=1$。
直接的计算显示$R=w_rw_l^T\in M_n$。

% ------------------------------------------------------------------------------
\section{Networks with Fixed or Switching Topology}
这部分，我们提出了三种主要的结论：i）描述了所有使用协议(\ref{A1})解决平均一致性问题的连接图。
ii）协议(\ref{A1})的性能和图的费德勒特征值（即代数连接）之间的联系。
iii）在切换拓扑下的连接失败/生成的鲁棒一致性问题。

@@

% ------------------------------------------------------------------------------
\section{Networks with Communication Time-Delays}
考虑固定拓扑$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$连续时间网络，其节点$i$的状态经过一个时滞$\tau > 0$的通信通道（或连接）达到节点$j$。
关于连接$ij$的转移函数表示如下：
\begin{equation}
    h_{ij}(s) = e^{-\tau_{ij}s}
    \notag
\end{equation}
应用线性时滞协议(\ref{A2})，网络动态变化可写作：
\begin{equation}
    \dot{x}_i(t) = \sum_{j\in N_i} a_{ij} [x_j(t-\tau_{ij}) - x_i(t-\tau_{ij})].
    \tag{37}
    \label{37}
\end{equation}
通过对公式(\ref{37})两边进行拉氏变换，我们得到
\begin{equation}
    sX_i(s) - x_i(0) = \sum_{j\in N_i} a_{ij} h_{ij}(s) (X_j(s) - X_i(s))
    \tag{38}
    \label{38}
\end{equation}
这里$X_i(s)$表示所有$i\in \mathcal{I}$中$x_i(t)$的拉氏变换。
公式的最后一部分可以写作如下紧凑形式：
\begin{equation}
    X(s) = (s+L(s))^{-1}x(0)
    \tag{39}
    \label{39}
\end{equation}
这里$L(x)$是图关于邻接矩阵$\mathcal{A}(s) = [a_{ij}h_{ij}(s)]$的拉普拉斯矩阵。
总的来说，任何关于通道$ij$的过滤效果都可以合并成连接转换函数$h_{ij}(s)$。
关于通信时滞智能体网络的协议(\ref{A2})收敛性分析减小为一个多输入多输出系统（MIMO）转移函数的稳定性分析
\begin{equation}
    G(s) = (sI+L(s))^{-1}.
    \notag
\end{equation}

@@

% ------------------------------------------------------------------------------
\section{Max-Consensus and Leader Determination}
在这部分，我们讨论带有一个唯一的最大领导者（max-leader）网络的最大一致性问题，即节点$i^*=\arg\max_ix_i(0)$。
最大一致性问题描述如下。
每一个智能体都有下述离散模型
\begin{equation}
    \tag{41}
    \label{41}
    x_i(k+1)=max(x_i(k),u_i(k))
\end{equation}
且被称作最大智能体（max-agent）。
最大智能体的动态等价描述为一个非线性离散时间系统如下：
\begin{equation}
    \tag{42}
    \label{42}
    x_i(k+1) = \frac{1}{2}(x_i(k)+u_i(k)+|x_i(k)-u_i(k)|)
\end{equation}
图$G=(\mathcal{V},\mathcal{E})$所有节点的值必须反复收敛到最大领导者的值。
另外，分布式的每一个节点都必须决定其是否是最大领导者。
最大一致性问题的一个应用是决定群组中的领导者（或协调者）具备关于特别兴趣量（例如，序列号，花费，高度，等等）的优先级，其必须执行或协调任务。

@@

% ------------------------------------------------------------------------------
\section{Simulation Results}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=12cm]{figures/Fig4-BalancedSC.jpeg}
    \label{Fig4}
    \caption{强连接的平衡图}
\end{figure}

@@

% ------------------------------------------------------------------------------
\section{Conclusions}
我们提供了具备有向信息流和固定或切换拓扑网络的一致性协议的收敛性分析。
我们的分析依赖于一些代数图论和矩阵论的工具。
我们建立了线性一致性协议的性质和镜像图拉普拉斯算子的费德勒特征值之间的联系。
介绍了简单的非一致性函数，其作为李雅普诺夫方程，允许切换拓扑网络的一致性协议的收敛性分析。
给出的交换图，该图表明了平衡图的加权邻接矩阵采用矩阵交换的拉普拉斯算子和对称部分矩阵的运算。
平衡图被证明对解决平均一致性问题是有帮助的。
